Determining Causes of Death with ChatGPT: A Case Study of Deaths from Verbal Autopsy in Sierra Leone from 2019-2022

### 2023-12-12 manuscript/manuscript.tex
Workin on bg

Most low-income countries have reported to have either no data or have registered less than 50\% of deaths in their country, where only 8\% of these deaths have a Cause of Death (COD) recorded \cite{worldhealthorganizationSCOREHealthData2021}. To increase the number of records with a COD, a method known as Verbal Autopsy (VA) is used to determine likely causes for deaths outside of healthcare facilities. VA involves trained interviewers that speak to those familiar with the deceased to gather information based on standard questionnaires and open narratives, and medical professionals that evaluate the information to assign probable CODs \cite{worldhealthorganizationVerbalAutopsyStandards2023}.

>>>>

Most low-income countries have reported to have either no data or have registered less than 50\% of deaths in their country, where only 8\% of these deaths have a Cause of Death (COD) recorded \cite{worldhealthorganizationSCOREHealthData2021}. To increase the number of records with a COD, a method known as Verbal Autopsy (VA) is used to determine likely causes for deaths outside of healthcare facilities. VA involves trained interviewers that speak to those familiar with the deceased to gather information based on standard questionnaires and open narratives, while medical professionals evaluate the information to assign probable CODs \cite{worldhealthorganizationVerbalAutopsyStandards2023}.
